Figure 2 and figure 2 supplementary material

### 2022-06-22 Figures/Figure2.Rmd
simplify wrapper corrplots input

################################################################################
wrapper_corrplots <- function(deconv_data, true_estimates, cancer_abreviation){
  # build the data
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))

>>>>

################################################################################
wrapper_corrplots <- function(deconv_data, true_estimates){
  # build the data
  true_subset_ <- true_estimates %>%  na.exclude() %>%
    arrange(factor(ParticipantBarcode, levels = ParticipantBarcode))
